% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage{fontspec} 
\usepackage{xunicode}
\usepackage{xltxtra}
% converts LaTeX specials (quotes, dashes etc.) to Unicode
\defaultfontfeatures{Mapping=tex-text}
\setromanfont [Ligatures={Common}, Numbers={OldStyle}]{Garamond}
% Cool ampersand
\newcommand{\amper}{{\fontspec[Scale=.95]{Garamond}\selectfont\itshape\&}}

% Set your name here
\def\name{Tahir H. Butt}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://tahirbutt.com/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {education},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={7.0in, 9.5in},
  left=0.75in,
  top=0.75in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  591 Ocean Avenue Apt 5G \\
  Brooklyn, NY 11226
  \end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (862) 368-6709 \\
    Email: & \href{mailto:me@tahirbutt.com}{\tt me@tahirbutt.com} \\
    Web: & \href{http://tahirbutt.com}{\tt tahirbutt.com} \\
  \end{tabular}
\end{minipage}


\section*{Education}

\begin{itemize}
    \item Doctoral candidate in Urban Education, The Graduate Center at the City University of New York, New York NY 2011--Present.
    \begin{itemize}
        \item Dissertation: Free Tuition and Access at the City University of New York, 1957-1976
        \item Advisor: Stephen Brier
    \end{itemize}
    \item Doctoral student in Cognitive and Linguistics Sciences, Brown University Providence, RI 2002--2004.
    \item Bachelors of Arts in Cognitive Science and Mathematics, Johns Hopkins University Baltimore, MD 1998--2002.
\end{itemize}

\section*{Teaching}

\begin{itemize}
    \item CUNY Graduate Center New York, NY, Digital Fellow, Fall 2016--Present.
      \begin{itemize}
        \item Support students and faculty with educational workshops and consultations for using technology for research and scholarship.
      \end{itemize}
    \item Computing Concepts Pilot at The Macaulay Honors College New York, NY, Teaching Assistant, Winter 2016.
      \begin{itemize}
        \item Supported visiting professor Zachary Dodd of Harvey Mudd College in an intensive 3-week pilot course for non-computer science majors to be introduced to computing through the Python programming language.
      \end{itemize}
    \item The Macaulay Honors College New York, NY, Instructional Technology Fellow, Fall 2013--Spring 2016.
      \begin{itemize}
        \item Responsible for supporting faculty and students in integrating technology into curriculum and student projects, using a Wordpress platform for developing course websites along with other open-source software.
      \end{itemize}
    \item Political Science department at Brooklyn College Brooklyn, NY, Graduate Teaching Fellow, Fall 2012--Spring 2013.
\end{itemize}

\section*{Professional}

\begin{itemize}
    \item Amplify Brooklyn, NY, Software Engineer, 2005--2016.
        \begin{itemize}
            \item Data engineer for product development 2011--2016.
            \item Software engineer for classroom tools and school reporting systems 2005--2011.
        \end{itemize}
\end{itemize}

\section*{Fellowships and awards}
\begin{itemize}
  \item Digital Fellow, Graduate Center Digital Initiatives at the Graduate Center of CUNY New York, NY. Fall 2016--Present
  \item Instructional Technology Fellow, Macaulay Honors College CUNY New York, NY. Fall 2013--Spring 2016
  \item Advanced Research Collaborative Student Fellow, CUNY Graduate Center New York, NY. Fall 2013--Spring 2014
  \item Enhanced Chancellor Fellow, CUNY Graduate Center New York, NY. Fall 2011--Spring 2012
  \item National Science Foundation IGERT Graduate Training Fellowship, Brown University Providence, RI. 2002--2004
\end{itemize}

\section*{Technical Skills}

\begin{itemize}
    \item Proficiency in application development with Python
    \item Proficiency in data analysis with Python, R, and SQL
    \item Proficiency in web programming using Javascript, PHP, HTML5, and CSS
\end{itemize}

\end{document}
